Meeting --- Summary LLM

### 2024-05-05 meetings/07-05-2024_slides.qmd
batching works
runs and slides

- Possible source for the spikes: The way the likelihoods are generated by the LLM.
  - We always select the respective token for each position in the target sequence.
  - However, if we generate a wrong token earlier in the sequence, then we select the probability of this token, given the wrong token.
  - Instead, we should still select the "chain" of probabilities for the target sequence
  - A possible solution: Apply a logits processor, that forces the model to always generate the correct sequence. Summary embedding that we train this way, still generate the target sequence with an unconstrained model, but should be more smooth to train!

"Transition scores for each vocabulary token at each generation step. Beam transition scores consisting of log probabilities of tokens conditioned on log softmax of previously generated tokens in this beam. Tuple of torch.FloatTensor with up to max_new_tokens elements (one element for each generated token), with each tensor of shape (batch_size*num_beams, config.vocab_size)." ([link](https://huggingface.co/docs/transformers/en/main_classes/text_generation#transformers.GenerationMixin.compute_transition_scores))

`.compute_transition_scores()` very similar to our functions; Computes the conditional probabilities for the generated sequence. Taking the sum, yields the likelihood of the generated sequence.

Does calling this function with the target sequence, yield the correct target likelihood?

>>>>

Found the source for the spikes and fixed it: `.generate()` is the wrong method, need `.forward()` $\to$ wrong conditionals! Now maximizes the likelihood and faster!

- New generated slogans seem better, space looks more interesting (have yet to do the "box" normalization)
- Maybe even further performance gains by using `past_key_values`

- Idea: LLM judge to assess grammar / quality of slogans?
- (MLFlow)

\textbf{Admin}:

- [ ] SLURM application
- [ ] Set appointment for pre-defense
- [ ] Find third assessor 
- [ ] Complete data management survey
